---
title: "DA401-API"
output: html_document
date: '2022-09-27'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("dplyr")
library(dplyr)
install.packages("Quandl")
library(Quandl)
```

Data Collection

The data from this project is pulled from Nasdaq data link using their API. If you register as a free user you will be given an API key to pull the data from their database.

Insert your API Key from Nasdaq data link website into quotation below
```{r}
Quandl.api_key("DD5KntqEEzVLo__LMXPs")
```

Data from "Federal Reserve Economic Data"
```{r}
gdp <- Quandl('FRED/GDP',collapse = "monthly", type = "raw")
cpiAuc <- Quandl('FRED/CPIAUCSL',collapse = "monthly", type = "raw")
fedFunds <- Quandl('FRED/DFF', collapse = "monthly",type = "raw")
treasuryYield10 <- Quandl('FRED/DGS10', collapse = "monthly",type = "raw")
treasuryYield3 <- Quandl('FRED/DTB3', collapse = "monthly",type = "raw")
treasuryYield30 <- Quandl('FRED/DGS30',collapse = "monthly", type = "raw")
unemployST <- Quandl('FRED/NROUST', collapse = "monthly",type = "raw")
unemployLT <- Quandl('FRED/NROU', collapse = "monthly",type = "raw")
unemployCivilian <- Quandl('FRED/UNRATE',collapse = "monthly", type = "raw")
saveRate <- Quandl('FRED/PSAVERT', collapse = "monthly",type = "raw")
disposeIncome <- Quandl('FRED/DSPI', collapse = "monthly",type = "raw")
disposeIncomeReal <- Quandl('FRED/DSPIC96', collapse = "monthly",type = "raw")
```

Data from "University of Michicgan Consumer Survey"
```{r}
consumerEconPol <- Quandl('UMICH/SOC34', collapse = "monthly",type = "raw")
consumerChangeIR <- Quandl("UMICH/SOC31", collapse = "monthly", type = "raw")
consumerChangePrice <- Quandl("UMICH/SOC32", collapse = "monthly", type = "raw")
consumerChangeUnemploy <- Quandl("UMICH/SOC30", collapse = "monthly", type = "raw")
consumerChangeBusiness <- Quandl("UMICH/SOC28", collapse = "monthly", type = "raw")
consumerIncStocks <- Quandl("UMICH/SOC20", collapse = "monthly", type = "raw")
consumerSentimentIndex <- Quandl("UMICH/SOC1", collapse = "monthly", type = "raw")
```

Uploading Bitcoin and U.S. Stock Market Index Data
```{r}


```

University of Michigan Data Alteration
```{r}


```

Aggregating Data to one Dataset
```{r}



```

