---
title: "DA401-API"
output: html_document
date: '2022-09-27'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("dplyr")
library(dplyr)
install.packages("Quandl")
library(Quandl)

```
```{r}
install.packages("lubridate")
library("lubridate")
```

Data Collection

The data from this project is pulled from Nasdaq data link using their API. If you register as a free user you will be given an API key to pull the data from their database.

Insert your API Key from Nasdaq data link website into quotation below
```{r}
Quandl.api_key("DD5KntqEEzVLo__LMXPs")
```

Data from "Federal Reserve Economic Data"
```{r}
gdp <- Quandl('FRED/GDP',collapse = "monthly", type = "raw")
cpiAuc <- Quandl('FRED/CPIAUCSL',collapse = "monthly", type = "raw")
fedFunds <- Quandl('FRED/DFF', collapse = "monthly",type = "raw")
treasuryYield10 <- Quandl('FRED/DGS10', collapse = "monthly",type = "raw")
treasuryYield3 <- Quandl('FRED/DTB3', collapse = "monthly",type = "raw")
treasuryYield30 <- Quandl('FRED/DGS30',collapse = "monthly", type = "raw")
unemployST <- Quandl('FRED/NROUST', collapse = "monthly",type = "raw")
unemployLT <- Quandl('FRED/NROU', collapse = "monthly",type = "raw")
unemployCivilian <- Quandl('FRED/UNRATE',collapse = "monthly", type = "raw")
saveRate <- Quandl('FRED/PSAVERT', collapse = "monthly",type = "raw")
disposeIncome <- Quandl('FRED/DSPI', collapse = "monthly",type = "raw")
equityUncertainty <- Quandl('FRED/WLEMUINDXD', collapse = "monthly",type = "raw")
policyUncertainty <- Quandl('FRED/USEPUINDXD', collapse = "monthly",type = "raw")
fedLoans <- Quandl('FRED/WLCFLL', collapse = "monthly",type = "raw")
oilPrice <- Quandl('FRED/OILPRICE', collapse = "monthly",type = "raw")
fedReservesBalance <- Quandl('FRED/WRESBAL', collapse = "monthly",type = "raw")

```

Data from "University of Michicgan Consumer Survey"
```{r}
consumerEconPol <- Quandl('UMICH/SOC34', collapse = "monthly",type = "raw")
consumerChangeIR <- Quandl("UMICH/SOC31", collapse = "monthly", type = "raw")
consumerChangePrice <- Quandl("UMICH/SOC32", collapse = "monthly", type = "raw")
consumerChangeUnemploy <- Quandl("UMICH/SOC30", collapse = "monthly", type = "raw")
consumerChangeBusiness <- Quandl("UMICH/SOC28", collapse = "monthly", type = "raw")
consumerIncStocks <- Quandl("UMICH/SOC20", collapse = "monthly", type = "raw")
consumerSentimentIndex <- Quandl("UMICH/SOC1", collapse = "monthly", type = "raw")
```

Uploading Bitcoin & Stock Market Data collected from Bloomberg terminal
```{r}
#getwd()
DependentVars <- read.csv("DATA/IndexData.csv")
DependentVars <- DependentVars[1:148,]
#str(DependentVar$Date)
```

convert short dates to long dates to match UMich data
```{r}
DependentVars$Date <- mdy(DependentVars$Date)
```

University of Michigan Data Alteration

Consumer evaluation in economic policy
```{r}
UMich <- data.frame(consumerEconPol$Date)
names(UMich)[names(UMich) == 'consumerEconPol.Date'] <- "Date"
consumerEconPol[,'EconomicPolicy'] <- NA
for (i in 1:nrow(consumerEconPol)){
  
  consumerEconPol$EconomicPolicy[i]= ((consumerEconPol$`Good Job`[i]/(consumerEconPol$`Good Job`[i]+consumerEconPol$`Fair Job`[i]+consumerEconPol$`Poor Job`[i])*3))+((consumerEconPol$`Fair Job`[i]/(consumerEconPol$`Good Job`[i]+consumerEconPol$`Fair Job`[i]+consumerEconPol$`Poor Job`[i]))*2)+((consumerEconPol$`Poor Job`[i]/(consumerEconPol$`Good Job`[i]+consumerEconPol$`Fair Job`[i]+consumerEconPol$`Poor Job`[i]))*1)

}
```

```{r}
UMich <- cbind(UMich, consumerEconPol["EconomicPolicy"])
```

Consumer Sentiment Index

```{r}
sentimentIndex <- consumerSentimentIndex[1:536,]
UMich <- cbind(UMich, sentimentIndex["Index"])
```

Consumer Inc Stocks --> use mean???
Do we want to use this variable because it decreases our observations in half???

```{r}
UMichStock <- UMich[1:242,]
UMichStock <- cbind(UMichStock, consumerIncStocks["Mean"])
names(UMichStock)[names(UMichStock)== "Mean"] <- "ExpectedStockIncrease"
```

Consumer expected change in unemployment

```{r}
consumerChangeUnemploy[,'ConsumerUnemployment'] <- NA
for (i in 1:nrow(consumerChangeUnemploy)){
  
  consumerChangeUnemploy$ConsumerUnemployment[i]= ((consumerChangeUnemploy$More[i]/(consumerChangeUnemploy$More[i]+consumerChangeUnemploy$Less[i]+consumerChangeUnemploy$Same[i])*3))+((consumerChangeUnemploy$Same[i]/(consumerChangeUnemploy$More[i]+consumerChangeUnemploy$Less[i]+consumerChangeUnemploy$Same[i]))*2)+((consumerChangeUnemploy$Less[i]/(consumerChangeUnemploy$More[i]+consumerChangeUnemploy$Less[i]+consumerChangeUnemploy$Same[i]))*1)

}

UMich <- cbind(UMich, consumerChangeUnemploy["ConsumerUnemployment"])
```

If we want to include stock increases
```{r}
ChangeUnemploy <- consumerChangeUnemploy[1:242,]
UMichStock <- cbind(UMichStock, ChangeUnemploy["ConsumerUnemployment"])
```

Consumer expected change in prices

```{r}
consumerChangePrice <- consumerChangePrice %>% rowwise() %>% mutate(More = sum(c_across(`Up by 1-2%`:`Up; DK how much`)))
#print(consumerChangePrice$More)
```

```{r}
consumerChangePrice[,'Prices'] <- NA
for (i in 1:nrow(consumerChangePrice)){
  
  consumerChangePrice$Prices[i]= ((consumerChangePrice$More[i]/(consumerChangePrice$More[i]+consumerChangePrice$Down[i]+consumerChangePrice$Same[i])*3))+((consumerChangePrice$Same[i]/(consumerChangePrice$More[i]+consumerChangePrice$Down[i]+consumerChangePrice$Same[i]))*2)+((consumerChangePrice$Down[i]/(consumerChangePrice$More[i]+consumerChangePrice$Down[i]+consumerChangePrice$Same[i]))*1)

}

UMich <- cbind(UMich, consumerChangePrice["Prices"])
```

If we want to include stock increases
```{r}
ChangePrice <- consumerChangePrice[1:242,]
UMichStock <- cbind(UMichStock, ChangePrice["Prices"])
```

Consumer expected change in interest rates

```{r}
consumerChangeIR[,'InterestRates'] <- NA
for (i in 1:nrow(consumerChangeIR)){
  
  consumerChangeIR$InterestRates[i]= ((consumerChangeIR$`Go Up`[i]/(consumerChangeIR$`Go Up`[i]+consumerChangeIR$`Go Down`[i]+consumerChangeIR$`Stay the Same`[i])*3))+((consumerChangeIR$`Stay the Same`[i]/(consumerChangeIR$`Go Up`[i]+consumerChangeIR$`Go Down`[i]+consumerChangeIR$`Stay the Same`[i]))*2)+((consumerChangeIR$`Go Down`[i]/(consumerChangeIR$`Go Up`[i]+consumerChangeIR$`Go Down`[i]+consumerChangeIR$`Stay the Same`[i]))*1)
}

UMich <- cbind(UMich, consumerChangeIR["InterestRates"])
```

If we want to include stock increases
```{r}
ChangeIR <- consumerChangeIR[1:242,]
UMichStock <- cbind(UMichStock, ChangeIR["InterestRates"])
```

Consumer expected change in business conditions

```{r}
consumerChangeBusiness[,'BusinessConditions'] <- NA
for (i in 1:nrow(consumerChangeBusiness)){
  
  consumerChangeBusiness$BusinessConditions[i]= ((consumerChangeBusiness$`Good Times`[i]/(consumerChangeBusiness$`Good Times`[i]+consumerChangeBusiness$`Bad Times`[i]+consumerChangeBusiness$Uncertain[i])*3))+((consumerChangeBusiness$Uncertain[i]/(consumerChangeBusiness$`Good Times`[i]+consumerChangeBusiness$`Bad Times`[i]+consumerChangeBusiness$Uncertain[i]))*2)+((consumerChangeBusiness$`Bad Times`[i]/(consumerChangeBusiness$`Good Times`[i]+consumerChangeBusiness$`Bad Times`[i]+consumerChangeBusiness$Uncertain[i]))*1)
}

UMich <- cbind(UMich, consumerChangeBusiness["BusinessConditions"])
```

If we want to include stock increases
```{r}
ChangeBC <- consumerChangeBusiness[1:242,]
UMichStock <- cbind(UMichStock, ChangeBC["BusinessConditions"])
```

```{r}
UMich2 <- UMichStock[1:231,]
```

Aggregating Fed data into one Dataset
```{r}

Fed <- data.frame(disposeIncome$Date)
Fed <- data.frame(Fed[1:231,])

save <- saveRate[1:231,]
disposable <- disposeIncome[1:231,]
CPI <- cpiAuc[1:231,]
FedFunds<- fedFunds[1:231,]
Treasury3 <- treasuryYield3[1:231,]
Treasury10 <- treasuryYield10[1:231,]
Treasury30 <- treasuryYield30[1:231,]
Civillian<- unemployCivilian[1:231,]
equity<- equityUncertainty[1:231,]
policy <- policyUncertainty[1:231,]
oil <- oilPrice[1:231,]
loans <- fedLoans[1:231,]
reserves <- fedReservesBalance[1:231,]

FederalReserve <- cbind(Fed,save$Value,disposable$Value,CPI$Value,FedFunds$Value,Treasury3$Value,Treasury10$Value, Treasury30$Value, Civillian$Value, equity$Value, policy$Value, oil$VALUE, loans$Value,reserves$Value)

```


Renaming columns in the aggregated Federal Reserve Data
```{r}
names(FederalReserve)[names(FederalReserve)== "Fed.1.231..."] <- "Date"
names(FederalReserve)[names(FederalReserve)== "saveRate$Value"] <- "SavingsRate"
names(FederalReserve)[names(FederalReserve)== "disposeIncome$Value"] <- "DisposableIncome"
names(FederalReserve)[names(FederalReserve)== "CPI$Value"] <- "CPI"
names(FederalReserve)[names(FederalReserve)== "FedFunds$Value"] <- "FederalFundsRate"
names(FederalReserve)[names(FederalReserve)== "Treasury3$Value"] <- "3YrTreasuryYield"
names(FederalReserve)[names(FederalReserve)== "Treasury10$Value"] <- "10YrTreasuryYield"
names(FederalReserve)[names(FederalReserve)== "Treasury30$Value"] <- "30YrTreasuryYield"
names(FederalReserve)[names(FederalReserve)== "Civillian$Value"] <- "Unemployment"
names(FederalReserve)[names(FederalReserve)== "equity$Value"] <- "EquityMktUncertainty"
names(FederalReserve)[names(FederalReserve)== "policy$Value"] <- "EconomicPolicyUncertainty"
names(FederalReserve)[names(FederalReserve)== "oil$VALUE"] <- "CrudeOilPrice"
names(FederalReserve)[names(FederalReserve)== "loans$Value"] <- "FederalReserveLoans"
names(FederalReserve)[names(FederalReserve)== "reserves$Value"] <- "FedReservesOnHand"

```

Merging the University of Michigan Data and the Federal Reserve Data
```{r}
IndependentVars <- merge(FederalReserve,UMich2, by = "Date")
```

Adding Bitcoin and Stock Index Data to independent Variables
```{r}
Data <- left_join(DependentVars,IndependentVars, join_by = "Date")
```

export to csv
```{r}
write.csv(Data,"BitcoinData.csv", row.names = FALSE)

```

See if you can get more recent 2022 data from FRED and UMICH for test set
--> available to look at on website but not being pulled for some reason



